\documentclass[10pt]{article}

%\usepackage{times}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\rhead{\textbf{Kód: pokles}}

\begin{document}

\subsection*{Zdroj:}

The Slovak Supreme Audit Office therefore asked the Tax Office of jurisdiction to perform a tax audit focused on VAT and income tax of legal entities for the fiscal years of 2002 and 2003.
6. According to the Czech Customs Database, a company dealing in imports and sales of cigarettes exported tobacco stamps valued at CZK 7.338,199.- in 2002 and CZK 12,228,545.- in 2003.
In its 2002 and 2003 VAT Return Forms, the company had not shown any exports.
The Czech Supreme Audit Office thus selected 5 export SADs (5 items), the aggregate statistical value of which was CZK2,471,598.-.
In the Slovak Customs Database, the Slovak Supreme Audit Office identified 7 matching SADs (7 items) in the aggregate statistical value of SK 2,919,514.-for 4 of the export SADs (4 items), the aggregate statistical value of which was CZK 2,246,860.-.
It was not possible to find a matching import SAD for one of the 5 export SADs (1 item) in the Slovak Customs Database, the statistical value of which was CZK 224,738.-.
7. A company dealing in software had not shown any exports in its 2002 and 2003 VAT Return Forms.
According to the Czech Customs Database, the aggregate statistical value of the exports in 2002 and 2003 was CZK 1,630,198.-.
The Czech Supreme Audit Office thus selected 9 SADs (9 items) for verification in the Slovak Republic, the aggregate statistical value of which was CZK 755,588.-.
In the Slovak Customs Database, the Slovak Supreme Audit Office identified 8 matching SADs (8 items) in the aggregate statistical value of SK 915,601.-.
It was not possible to find a matching import SAD for one of the 9 export SADs (1 item) in the Slovak Customs Database, the statistical value of which was CZK 68,286.-.
In the cases listed above, it was not possible to find matching imports to 6 export SADs, the aggregate statistical value of which was CZK 692,800.-, in the Slovak Customs Database.


Of these:

- It was not possible to find matching import SADs for 2 export SADs registered in the Czech Customs Database, the aggregate statistical value of which was CZK 293,024.-, in the Slovak Customs Database (see Paragraphs 6 and 7 above).


\pagebreak

\subsection*{Překlad:}

Nejvyšší kontrolní úřad proto požádal Finanční úřad příslušného k provedení daňové kontroly zaměřené na DPH a daň z příjmů právnických osob za účetní období 2002 a 2003.
6. Podle České celní databáze společnost zabývající se dovozem a prodejem cigaret exportovala tabákové nálepky v hodnotě 7,388,199, - Kč v roce 2002 a 12,228,545, - Kč v roce 2003.
Ve formulářích pro přiznání k DPH z roku 2002 a 2003 společnost neprokázala žádný vývoz.
Nejvyšší kontrolní úřad tak vybral 5 exportních SAD (5 položek), jejichž celková statistická hodnota činila 2 471 598 Kč.
Ve Slovenské celní databázi identifikoval slovenský Nejvyšší kontrolní úřad 7 odpovídajících SAD (7 položek) v souhrnné statistické hodnotě 2 919 514, - pro 4 exportních JSD (4 položky), jejichž celková statistická hodnota byla 2 246 860 Kč. -.
Nebylo možné nalézt odpovídající importní SAD pro jeden z 5 exportních JSD (1 položka) ve Slovenské celní databázi, jejíž statistická hodnota činila 224 738 Kč.
7. Společnost, která obchoduje se softwarem, nevykazovala žádný vývoz ve svých formulářích pro přiznání k DPH z roku 2002 a 2003.
Souhrnná statistická hodnota vývozu v letech 2002 a 2003 byla podle České celní databáze 1 630 198 Kč.
Nejvyšší kontrolní úřad tak v České republice vybral 9 SAD (9 položek) pro ověřování, jejichž celková statistická hodnota byla 755 588 Kč.
Ve Slovenské celní databázi identifikoval Nejvyšší kontrolní úřad Slovenské republiky 8 odpovídajících SAD (8 položek) v celkové statistické hodnotě 915 601 Kč.
Nebylo možné nalézt odpovídající importní SAD pro jeden z 9 exportních SAD (1 položka) ve Slovenské celní databázi, jejíž statistická hodnota byla 68 286 Kč.
Ve výše uvedených případech nebylo možné nalézt odpovídající dovoz na 6 exportních JSD, jejichž souhrnná statistická hodnota byla ve slovenské celní databázi 692 800 Kč .-.


Z nich:

- Nebylo možné nalézt odpovídající importní SAD pro 2 exportní SAD registrované v České celní databázi, jejichž souhrnná statistická hodnota činila 293 024, - Kč ve Slovenské celní databázi (viz body 6 a 7 výše).


\end{document}
