\documentclass[10pt]{article}

%\usepackage{times}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\rhead{\textbf{Kód: biograf}}

\begin{document}

\subsection*{Zdroj:}



Comprehensiveness of specifications

In most of the cases reviewed, the tender documents had been fully elaborated before the process of soliciting bids was launched.
However in various cases, documents had to be modified during the tendering process to pay due regard to changing items or time schedules.
In isolated cases, tender documents contained work or supplies whose necessity was uncertain.
One tender document on demolition work we looked at consisted almost exclusively of such items.


Lots and criteria according to which the contract is to be awarded

In a large number of cases, the required justification for not subdividing the lots of services into partial lots was not given.
The criteria we studied according to which the contract is to be awarded gave us no reason to point out shortcomings.


Inclusion of names of self-employed professionals

In a number of documents the commissioned independent professionals involved were mentioned.
The names were identified on the cover sheets or on the plans or opinions attached.
In one case, the contracting authority even called upon bidders to contact the architect explicitly mentioned regarding questions on the tender.
In building construction projects such cases were caused in the first place by the self-employed persons commissioned to develop the specification documents.
The building administration services stated that they did not have enough staff to control the tender documents in detail.


NKÚ



Technical specifications and product-neutral invitation to tender

In case of public procurement for 12 apartments building, there was reference to concrete supplier and type of product mentioned in the specification.
Contracting authority did not admit using of other comparable types of products. and did not give reason for insisting on these concrete suppliers and products.
In connections with the constructing of various university facilities, the tender documents specified concrete suppliers and products.


Overall list of specifications with partial specifications

In case of constructions of some industrial zones contracting authority did not clearly specify the volume and type of requested works and supplies in the list of measurement, and as measuring unit he specified for each building only the built up volume in cubic meters.


Comprehensiveness of specifications

During the procurement of public contract for construction of a road circle, the tender documentation for restricted procedure was four times changed in the period of August– September 2009.


\pagebreak

\subsection*{Překlad:}



Úplnost specifikací

Ve většině zkoumaných případů byly zadávací dokumentace plně vypracovány před zahájením procesu podávání nabídek.
V různých případech však musely být dokumenty během nabídkového řízení upraveny tak, aby náležitě zohledňovaly měnící se položky nebo časové plány.
V ojedinělých případech obsahovaly zadávací dokumentace práci nebo dodávky, jejichž nezbytnost byla nejistá.
Jeden uchazeč o práci na demolici, na kterou jsme se dívali, spočíval téměř výlučně v těchto bodech.


Šarže a kritéria, podle nichž má být zakázka zadána

Ve velkém počtu případů nebylo uvedeno požadované odůvodnění pro nerozdělicování částí služeb na dílčí šarže.
Kritéria, která jsme studovali, podle nichž má být zakázka zadána, nám nedala žádný důvod poukázat na nedostatky.


Zahrnutí jmen osob samostatně výdělečně činných

V řadě dokumentů se zmínili pověření nezávislí odborníci.
Názvy byly uvedeny na titulní straně nebo na připojených plánech nebo stanoviscích.
V jednom případě zadavatel dokonce vyzval uchazeče, aby kontaktovali výslovně uvedeného architekta ohledně otázek týkajících se nabídky.
V rámci stavebních projektů byly tyto případy způsobeny především osobami samostatně výdělečně činnými, které byly pověřeny vypracováním zadávací dokumentace.
Útvary správy budov uvedly, že nemají dostatek zaměstnanců, aby mohly zadávací dokumentaci podrobně kontrolovat.


NKÚ



Technické specifikace a nabídkové řízení neutrální z hlediska výrobků

V případě veřejných zakázek na 12 bytů byl uveden odkaz na konkrétního dodavatele a typ výrobku uvedený ve specifikaci.
Veřejný zadavatel nepřipustil použití jiných srovnatelných typů výrobků. a neposkytl důvod trvat na těchto konkrétních dodavatelích a výrobcích.
V souvislosti s vytvářením různých univerzit byly v zadávací dokumentaci uvedeny konkrétní dodavatelé a produkty.


Celkový seznam specifikací s dílčími specifikacemi

V případě staveb některých průmyslových zón zadavatel v seznamu měření jasně neuvádí objem a typ požadovaných stavebních prací a dodávek a jako měřicí jednotka pro každou budovu stanovil pouze objem postavený v krychlových metrech.


Úplnost specifikací

Během zadávání veřejných zakázek na výstavbu silničního okruhu byla dokumentace nabídkového řízení pro omezené řízení v období od srpna do září 2009 čtyřikrát změněna.


\end{document}
