\documentclass[10pt]{article}

%\usepackage{times}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\rhead{\textbf{Kód: jistota}}

\begin{document}

\subsection*{Zdroj:}

Entities handling monitored mineral oils either in bulk storage or in packaging exceeding 220 litres must be registered with the duty administrator.
For the registration to be issued, the applicant, the governing body, and the responsible representative have to meet the stipulated personal conditions, and these have to be satisfied for the duration of the registration.


THISsegmentISintentionallyLEFTblank



THISsegmentISintentionallyLEFTblank



THISsegmentISintentionallyLEFTblank

As at 30 November 2016, the registry of persons authorised to handle mineral oils contained 54 valid registrations; four registrations were cancelled on the request of the registration holders themselves.
Electronic records have to contain detailed information about income, own consumption, and sale or movement of mineral oils, including document numbers, numbers of the notifications of receipt sent to the excise duty administrator, storage and consumption sites, purpose of consumption, or, in the case of sale, place of delivery (destination) and customer registration number.
The excise duty administrator has to receive notifications of each receipt of special mineral oils 24 to 72 hours prior to the receipt.
The notification must include identification of the business partners, name and nomenclature of each special mineral oil, amount, purpose of consumption or sale/transfer information.
Notification of the expected amount of mineral oil to be purchased, sold or consumed in the respective year must be submitted by the entity at the time of submission of the registration application or by the end of the respective calendar year.
Notifications of the purpose of use and marking, storage, or consumption site, and identification data about the person to whom the special mineral oil is sold or transferred are to be submitted before each change of such information.
Notifications are submitted electronically using intelligent forms or via data box in PDF format.
A total of 630 notifications were submitted by persons handling special mineral oils during the audited period.
An excise duty administrator has to confiscate and forfeit special mineral oils or the transport vehicle when he discovers that special mineral oils are being handled without registration or if the registered person is not fulfilling his notification obligations.
Just like the case of failure to fulfil obligations connected to the transport/movement of excisable goods, these shortcomings cannot be remedied after the fact.
Fuel distributor registration is mandatory for persons who sell or are authorised to sell fuel.


\pagebreak

\subsection*{Překlad:}

Subjekty, které nakládají se sledovanými minerálními oleji buď ve volně loženém stavu, nebo v obalech s objemem vyšším než 220 litrů, musí být registrovány u správce daně.
Pro vydání registrace musí žadatel, řídící orgán a odpovědný zástupce splnit stanovené osobní podmínky, které musí být po celou dobu registrace splněny.


THISsegmentISintentionallyLEFTblank



THISsegmentISintentionallyLEFTblank



THISsegmentISintentionallyLEFTblank

Registr osob oprávněných nakládat s minerálními oleji k 30. listopadu 2016 obsahoval 54 platných registrací; čtyři registrace byly zrušeny na žádost samotných držitelů registrace.
Elektronické záznamy musí obsahovat podrobné informace o příjmech, vlastní spotřebě a prodeji nebo pohybu minerálních olejů, včetně čísel dokladů, čísel oznámení o přijetí zasílaných správci spotřební daně, místům skladování a spotřeby, účelem spotřeby nebo v případě prodeje, místa dodání (místa určení) a registračního čísla zákazníka.
Správce spotřební daně musí obdržet oznámení o každém obdržení speciálních minerálních olejů 24 až 72 hodin před převzetím.
Oznámení musí obsahovat identifikaci obchodních partnerů, název a nomenklaturu každého speciálního minerálního oleje, množství, účel spotřeby nebo informace o prodeji / převodu.
Oznámení o očekávaném množství minerálního oleje, který má být zakoupen, prodán nebo spotřebován v daném roce, musí subjekt předložit v době podání žádosti o registraci nebo do konce příslušného kalendářního roku.
Oznámení o účelu použití a značení, skladování nebo spotřeby a identifikačních údajích o osobě, které je speciální minerální olej prodáván nebo převáděn, musí být předloženy před každou změnou těchto informací.
Oznámení se zasílají elektronicky pomocí inteligentních formulářů nebo prostřednictvím datové schránky ve formátu PDF.
V průběhu sledovaného období podaly osoby, které nakládaly se speciálními minerálními oleji, celkem 630 oznámení.
Správce spotřební daně musí zabavit a propadnout speciální minerální oleje nebo dopravní prostředek, pokud zjistí, že se s minerálními oleji zachází bez registrace nebo pokud registrovaná osoba neplní své oznamovací povinnosti.
Stejně jako v případě nesplnění povinností spojených s přepravou / přepravou zboží podléhajícího spotřební dani nelze tyto nedostatky napravit ani po této skutečnosti.
Registrace distributorů pohonných hmot je povinná pro osoby, které prodávají nebo jsou oprávněny prodávat palivo.


\end{document}
